The problem and promise of scale in multilayer networks

### 2020-02-04 paper/manuscript.Rmd
edits to case study results/discussion

We observed variation in multilayer network metrics as a function of changes in social, spatial, and temporal scale. 
<!-- TODO: make sure we clarify these are means of all individuals? -->

In general, individuals in multilayer networks became more connected as a
function of social scale, however, this relationship varied by habitat type and
season. As social scale increased, connective redundancy increased rapidly when
groups were formed based on ~100m threshold, followed by a plateau and slight
decrease at higher thresholds, presumably due to an increase in summer forest
degree at ~500m (Figure \@ref(fig:socres)b). Regardless of social scale, layer
relevance did not change for any habitat types or seasons, which suggests
habitat-by-season layers captured most, if not all, of the potential connections
and individual would have across all networks (Figure \@ref(fig:socres)c).
Finally, somewhat predictably, graph strength for winter networks increased up
to ~100-200m thresholds, followed by a plateau, while graph strength for summer
networks did not change as the social threshold increased (Figure
\@ref(fig:socres)d).  Taken together, these results suggest the optimal social
scale at which groups should be assigned is likely somewhere between ~20-100m
based on the rate at which network metrics stabilized. For ungulates, groups are
often assigned based on 50m threshold (Lingle 2003; Lesmeries et al. 2018;
Peignier et al. 2019), suggesting that given similar quantities of data, ~50m is
likely an ideal social scale for generating social networks in caribou and
similar species.

<!-- landcover resolution
* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
* decreasing winter lichen relevance because the degree + number of edges decreased
-->

Larger landcover resolution scale resulted in decreased proportion of rare and
patchy habitats and low connectivity of individuals in these habitats. In
winter, layer relevance was stable for open and forest habitats but decreased
for forage habitats (Figure \@ref(fig:lcres)c). Connective redundancy decreased
with increasing landcover resolution due the decrease in connectivity of
individuals in winter forage habitats, resulting in a multilayer network where
neighbours were less frequently repeated in multiple layers (Figure
\@ref(fig:lcres)b). Layer similarity was generally stable for forest and open
habitats except for a contrasting increase in similarity for forest and decrease
in similarity for open habitats at 250m landcover resolution (Figure
\@ref(fig:lcres)a). Layer similarity was not possible to calculate between
winter and summer forage because, at all landcover resolutions greater than 10m
there were no individuals connected in the network layers. <!-- individuals
still used forage but in much lower proportion + lowered opportunity to
associate --> These results indicate the importance of matching landcover
resolution to scale of selection as well as ensuring the landcover product used
has a resolution fine enough to detect relevant landscape features and habitats.

@@

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics generally appeared to stabilize.
Like coarse landcover resolution (above), low number of observations were not
sufficient for capturing individuals in all contexts and layer similarity could
not be calculated below ~75 observations for forest, ~210 observations for open
and ~300 observations for forage (Figure \@ref(fig:nobs)a). Once sufficient
observations were used, layer similarity stabilized with additional for all
three landcover classes at ~200 observations for forest, ~300 observations for
open and forage. Connective redundancy increased with increasing number of
observations as individuals became more connected to neighbours in multiple
layers (Figure \@ref(fig:nobs)b). Given the overall trend of these multilayer
metrics stabilizing after a certain number of observations are included, the
results suggest this sensitivity method could be useful for determining the
number of observations necessary for sufficiently describing the social dynamics
across contexts.

@@

Contrasting winter and summer seasons became more similar with increasing window
length. Layer similarity between seasons increased consistently across landcover
class (Figure \@ref(fig:winlen)a). Individual graph strength and layer relevance
increased for all summer layers as individuals became more connected with
increasing window lengths (Figure \@ref(fig:winlen)c, Figure
\@ref(fig:winlen)d). These results suggest that an increasing window length,
especially for the summer season, may be resulting in less precisely defined
seasons that are not clearly capturing periods of aggregation and
dissaggregation according to resource availability and presence of conspecifics.
Similarly,

@@

Shifting window position results showed increasing layer similarity

>>>>

<!-- TODO: make sure we clarify these are means of all individuals? -->

<!-- TODO: discuss layer similarity for social threshold -->
In general, individuals in multilayer networks became more connected as social scale 
increased; however, this relationship varied by habitat type and
season. As social scale increased, connective redundancy increased rapidly when
groups were formed up to approximately 100m threshold, followed by a plateau and slight
decrease at higher thresholds, presumably due to an increase in summer forest
degree at ~500m (Figure \@ref(fig:socres)b). Regardless of social scale, layer
relevance did not change for any habitat types or seasons, which suggests
habitat-by-season layers captured most, if not all, of the potential connections
an individual would have across all networks (Figure \@ref(fig:socres)c).
Finally, somewhat predictably, graph strength for winter networks increased up
to ~100-200m thresholds, followed by a plateau, while graph strength for summer
networks did not change as the social threshold increased (Figure
\@ref(fig:socres)d).  Taken together, these results suggest the optimal social
scale at which groups should be assigned is likely somewhere between ~20-100m
based on the rate at which network metrics stabilized. For ungulates, groups are
often assigned based on 50m threshold (Lingle 2003; Lesmeries et al. 2018;
Peignier et al. 2019), suggesting that given similar quantities of data, ~50m is
likely an ideal social scale for generating social networks in caribou and
similar species.

<!-- landcover resolution
* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
* decreasing winter lichen relevance because the degree + number of edges decreased
--> 
<!-- TODO: discuss things in a,b,c,d order consistently. They shouldn't be presented out of order -->
Increasing the scale of landcover resolution resulted in decreased proportion of rare and
patchy habitats and low connectivity of individuals in these habitats. In
winter, layer relevance was stable for open and forest habitats but decreased
for forage habitats (Figure \@ref(fig:lcres)c). Connective redundancy decreased
with increasing landcover resolution due the decrease in connectivity of
individuals in winter forage habitats, resulting in a multilayer network where
neighbours were less frequently repeated in multiple layers <!-- TODO: I'm having a hard 
time understanding this previous sentence --> (Figure\@ref(fig:lcres)b). Layer similarity 
was generally stable for forest and open
habitats except for a contrasting increase in similarity for forest and decrease
in similarity for open habitats at 250m landcover resolution (Figure
\@ref(fig:lcres)a). Layer similarity was not possible to calculate between
winter and summer forage because, at all landcover resolutions greater than 10m
there were no individuals connected in the network layers. <!-- individuals
still used forage but in much lower proportion + lowered opportunity to
associate --> These results indicate the importance of matching landcover
resolution to scale of selection as well as ensuring the landcover product used
has a resolution fine enough to detect relevant landscape features and habitats. <!-- TODO: how? This isn't clear enough for me to follow yet -->

@@

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics generally appeared to stabilize.
Like coarse landcover resolution (above), low numbers of observations were not
sufficient for capturing individuals in all contexts and layer similarity could
not be calculated below approximately 75 observations for forest, approximately 210 
observations for openand approximately 300 observations for forage (Figure 
\@ref(fig:nobs)a). Once sufficient observations were obtained, layer similarity stabilized 
for all three landcover classes at approximately 200 observations for forest and approximately 300 observations for open and forage landcover types. Connective redundancy increased with increasing number of
observations as individuals became more connected to neighbours in multiple
layers (Figure \@ref(fig:nobs)b). Given the overall trend of these multilayer
metrics stabilizing after a certain number of observations are included, the
results suggest this sensitivity method could be useful for determining the
number of observations necessary for sufficiently describing the social dynamics
across contexts. <!-- TODO: I'm not sure this is relevant since this is the main way it is already done, can we make this thought more relevant to picking scales or multilayer networks in general? I think it's important for building robust networks -->

@@

Contrasting winter and summer seasons became more similar with increasing window
length. Layer similarity between seasons increased consistently across landcover
class (Figure \@ref(fig:winlen)a). Individual graph strength and layer relevance
increased for all summer layers as individuals became more connected with
increasing window lengths (Figure \@ref(fig:winlen)c, Figure
\@ref(fig:winlen)d). These results suggest that an increasing window length,
especially for the summer season, may be resulting in less precisely defined
seasons that are not clearly capturing periods of aggregation and
dissaggregation according to resource availability and presence of conspecifics.
Similarly,<!-- TODO: ?? -->
<!-- TODO: end with something highlighting this shows it's important to properly define your season -->

@@

Shifting window position results showed increasing layer similarity 
<!-- TODO: haha, good conclusion -->
